\plaintitle

### 2016-08-11 drafts/labor/cases.tex
wednesday edits

@@

\subsection{What are the limits of crowdsourcing?}
For more than a decade
research in crowd work has explored ways of expanding the work that crowdsourcing can do by
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes,
and repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been whether there are limits to crowdsourcing
(and, if so, what bounds them).

In the field of piecework,
the research covering this topic has both explored
a breadth of tasks that might be rendered doable by piecemeal workers
\textit{as well as} longitudinally documented the success of these approaches.

\subsection{The Processes of Making Gig(s) Work}\label{sec:MakingGigsWork}
The HCI community is perhaps most familiar with examples of task--based work such as
99designs,
Amazon Mechanical Turk (AMT),
and increasingly
Uber \& Lyft,
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.

This section will largely discuss the processes at work that make distributed,
digitally managed work both possible and indeed preferable for ``requesters''
(in other words, the employers who solicit workers).
This body of research spans a broad field
within the CSCW and broader HCI community.
In this context,
we'll look at the body of research through the lens of
highlighting contributions which expand what we
(as ``requesters'' of work) can do by managing workers in novel ways.
This work broadly consists of three areas:
\begin{inlinelist}
\item \nameref{sec:decomposition},
\item \nameref{sec:workAbstraction}, and
\item \nameref{sec:flexibility}
\end{inlinelist}.
As we explore this work, we'll
attempt to relate the advances in the design of crowd work to
the research contributions made in the research of assembly line manufacturing,
Taylorism, and
scientific management 
during the \nth{20} century
\cite{hu1961parallel}.

\subsubsection{Decomposition}\label{sec:decomposition}
Piecework may be thought of as vertically slicing work such that 
each person is responsible for the whole task
--- making a whole garment, in this case.
Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example,
it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

@@

Scholarship describing and exploring
the decomposition of tasks is perhaps the most established of the above areas among HCI researchers;
\citeauthor{crowdForgeKittur} specifically drive at this goal by addressing the possibility of
``crowdsourcing complex work''
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work might be readily interrupted
\cite{cheng2015break}.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work
by exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While this work doesn't strictly fall under ``crowdsourcing'',
the major contributions here
seem uncontroversially to be inspired by the design of crowd work.

Work decomposition, then, is far from new;
``decomposition'' generally illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger and warned of it in
\citeyear{professionalCrowdworkEthics}
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in his documentary work
% \citetitle{riisOtherSideLives}
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

@@

>>>>

% lol oh my gosh i just discovered figlet and it's changing my life
% it's like i'm distributing warez

@@

%  _ _           _ _                __ 
% | (_)_ __ ___ (_) |_ ___    ___  / _|
% | | | '_ ` _ \| | __/ __|  / _ \| |_ 
% | | | | | | | | | |_\__ \ | (_) |  _|
% |_|_|_| |_| |_|_|\__|___/  \___/|_|

%                            _                          _             
%   ___ _ __ _____      ____| |___  ___  _   _ _ __ ___(_)_ __   __ _ 
%  / __| '__/ _ \ \ /\ / / _` / __|/ _ \| | | | '__/ __| | '_ \ / _` |
% | (__| | | (_) \ V  V / (_| \__ \ (_) | |_| | | | (__| | | | | (_| |
%  \___|_|  \___/ \_/\_/ \__,_|___/\___/ \__,_|_|  \___|_|_| |_|\__, |
%                                                               |___/

\subsection{What are the limits of crowdsourcing?}
Research in crowdsourcing has spent the better part of a decade
exploring ways of growing the limits of crowdsourcing and
finding the boundaries of crowd work and microtasks;
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes,
and repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:decomposition},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
% We will further discuss the ways that various contributions drive along these dimensions.
As we'll discuss through these dimensions,
exploring the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition,
we'll also point to corresponding piecework literature addressing these aspects;
finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

\ali{At this point I'm trying to retain as much of the old content as possible,
but if the next few sections seem like I'm trying too hard to be lazy,
say so and I'll do a rewrite rather than refactoring.}

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
% lol i can't believe this worked i'm going to do this with every section.

\subsubsection{Decomposition}\label{sec:decomposition}
Scholarship describing and exploring
the decomposition of tasks is perhaps the most established
of the previously mentioned three areas
to HCI researchers;
\citeauthor{crowdForgeKittur} specifically drive at this goal by addressing the possibility of
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.

Research exploring the decomposition of work more generally
--- that is, without the constraint of an employer/requester directing workers ---
has since emerged as well.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the topicality of this broader body of work will become more apparent
as we trace the parallels of crowdsourcing with piecework.

The work described thus far has illustrated myriad ways that
we can manage workers for the purpose of accomplishing complex tasks with
rapidly sourced workers from across the world.
Critically, the work's defining characteristic involves
the use of the Internet as a medium both 
to coordinate workers, as well as
to do the work itself.
But research into the ``decomposition'' of work more generally
illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger and warned of it in
\citeyear{professionalCrowdworkEthics}
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

Following this thread of work, it may be said that
much of the work in crowdsourcing has found ways of ``vertically slicing'' work
such that each person is responsible for as small a task as can be made reasonable
--- taking a minute of audio, for instance, and transcribing just that.
The aforementioned research has found many novel ways to slice work,
communicate different amounts of context of work from one worker to the next,
etc\dots
but fundamentally they follow similar patterns.
It's through this lens that we see the echoes of piecework.

%                        _ _      _ 
%  _ __   __ _ _ __ __ _| | | ___| |
% | '_ \ / _` | '__/ _` | | |/ _ \ |
% | |_) | (_| | | | (_| | | |  __/ |
% | .__/ \__,_|_|  \__,_|_|_|\___|_|
% |_|

Piecework Piecework Piecework Piecework Piecework Piecework Piecework

% Piecework's growing popularity was best documented at the turn of the \nth{20}
% by \citeauthor{riisOtherSideLives} % in his work on \citetitle{riisOtherSideLives}
% \cite{riisOtherSideLives}.

Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example,
it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

@@

%                     _            _         _                  _   _             
% __      _____  _ __| | __   __ _| |__  ___| |_ _ __ __ _  ___| |_(_) ___  _ __  
% \ \ /\ / / _ \| '__| |/ /  / _` | '_ \/ __| __| '__/ _` |/ __| __| |/ _ \| '_ \ 
%  \ V  V / (_) | |  |   <  | (_| | |_) \__ \ |_| | | (_| | (__| |_| | (_) | | | |
%   \_/\_/ \___/|_|  |_|\_\  \__,_|_.__/|___/\__|_|  \__,_|\___|\__|_|\___/|_| |_|
% lollllllllllllllll

@@

In the field of piecework,
the research covering this topic has both explored
a breadth of tasks that might be rendered doable by piecemeal workers
\textit{as well as} longitudinally documented the success of these approaches.
Here, we
